---
title: "Asg3"
author: "Christine Gormley"
date: '`r Sys.Date()` '
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
getwd()
```



# Q 1

# 5.54 Pg. 215


a.  Worked out on separate paper. 




b. Yes, the data do appear to follow an exponential distribution of $\beta=95$ because in an exponential probability distribution $\mu=\beta$ and the $\mu$ is 95 in this case. 




# Q 2 

# 5.56 pg. 215 

solved for gamma(2)

```{r}
gamma(2)
```



a. Work on separate paper. 

b. Work on separate paper. 


# Q 3 

# 5.60 pg. 216 

a. Work on separate paper. 

b. Work on separate paper. 

# Q 4 

# 5.74 pg. 219 

Calculating gamma(1.5)

```{r}
gamma(1.5)
```

# Q 5 

# 5.84 pg. 223 

Work on separate paper. 

# Q 6 5.114 pg. 232 

Work on separate paper. 

# Q 7 

a. Work on separate paper. 

b. Work on separate paper. 

# Q 8

Work on separate paper. 

# Q 9

Work on separate paper. 

# Q 10 

Work on separate paper. 

# Q 11 

Worn on separate paper. 


# Q 14 

confidence interval 

```{r}
leadcopp = read.csv("LEADCOPP.csv")
head(leadcopp)
```
## A 

```{r}
t.test(leadcopp$ï..LEAD,conf.level= 0.99)
```

## B 

```{r}
t.test(leadcopp$COPPER, conf.level = 0.99)
```

## C 

The confidence interval for lead in the specimens of water is (-1.14, 6.919) meaning there is confidence that lead levels fall between these two numbers in the sampled water. 

There is confidence that the copper levels in the sampled water lies in the interval (0.1518, 0.66472). 

## D 

99% confidence means that there is a 99% likelihood that the mean of the copper and lead levels fall within the intervals from c. 

# Q 15 

Find 95% confidence level for the mean difference between the day-long clear-sky solar irradiation levels. This is a paired sample. 

```{r}
solarad = read.csv("SOLARAD.csv")

with(solarad, t.test(IOWA, STJOS, paired = TRUE, conf= 0.95))
```



# Q 16 

## A 

```{r}
diazinon = read.csv("DIAZINON.csv")

with(diazinon, t.test(DAY, NIGHT, paired = TRUE, conf= 0.95))
```

The 90% confidence interval that describes how day and night differ is (-63.48,-14.33440)

## B 

Some assumptions that have to be made for part a to be valid is that the samples are independent and they are a normal distribution. 

## C 

The mean difference is -38.90 meaning there is always some difference between day and night. 




```{r}
set.seed(24); y1 = rnorm(30, 10, 5)
set.seed(34); y2 = rnorm(25, 11, 5)

t.test(y1,y2, var.equal = TRUE, mu =0, conf.level = 0.95)
```




