---
title: "Lab9"
author: "Christine Gormley"
date: "3/30/2022"
output: 
    html_document:
     toc: yes
     toc_float: yes

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 1 

```{r}
getwd()
```
# Task 2 

Line A means that if x be a vector or array the sample will take n*iter points from x with replacement. 

Line B forms a confidence interval with xstate vector and and boundaries given as a c() function. 

Equal distribution 


```{r}
set.seed(35) # This will give everyone the same sample
sam=round(rnorm(20,mean=10,sd=4),2) 

```

```{r}
unique(sample(sam,20,replace=FALSE) ) # repeat this line 5Xs
```




```{r, eval=FALSE}
sample(sam,21,replace=FALSE) 
```
The sample function  an error because the sample in this function is bigger than the population which is 20.  


# Task 3


```{r}
myboot2<-function(iter=10000,x,fun="mean",alpha=0.05,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

invisible(list(ci=ci,fun=fun,x=x))# Some output to use if necessary
}


set.seed(39); sam=rnorm(25,mean=25,sd=10)
windows();myboot2(10000,x=sam,fun="mean",alpha=0.05,xlab="mean",col="Purple",cx=1.5) # mac quartz()

## quantile
alpha=0.05
qnorm(1-alpha/2)
qnorm(alpha/2)


```

```{r}
myboot2<-function(iter=10000,x,fun="mean",alpha=0.05,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

invisible(list(ci=ci,fun=fun,x=x))# Some output to use if necessary
}

set.seed(30); sam=rchisq(20,df=3)
windows();myboot2(10000,x=sam,fun="mean",alpha=0.05,xlab="mean",col="Purple",cx=1.5) # mac quartz()

## quantile
alpha=0.05
qnorm(1-alpha/2)
qnorm(alpha/2)

```





```{r}
myboot2<-function(iter=10000,x,fun="mean",alpha=0.05,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

invisible(list(ci=ci,fun=fun,x=x))# Some output to use if necessary
}

set.seed(40); sam=rgamma(30,shape=2,scale=3)
windows();myboot2(10000,x=sam,fun="mean",alpha=0.05,xlab="mean",col="Purple",cx=1.5) # mac quartz()

## quantile
alpha=0.05
qnorm(1-alpha/2)
qnorm(alpha/2)
```


```{r}
myboot2<-function(iter=10000,x,fun="mean",alpha=0.05,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

invisible(list(ci=ci,fun=fun,x=x))# Some output to use if necessary
}

set.seed(10); sam=rbeta(20,shape1=3,shape2=4)


windows();myboot2(10000,x=sam,fun="mean",alpha=0.05,xlab="mean",col="Purple",cx=1.5) # mac quartz()

## quantile
alpha=0.05
qnorm(1-alpha/2)
qnorm(alpha/2)

```



# 80% bootstrap intervals 

```{r}
myboot2<-function(iter=10000,x,fun="population variance",alpha=0.02,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

invisible(list(ci=ci,fun=fun,x=x))# Some output to use if necessary
}

set.seed(39); sam=rnorm(25,mean=25,sd=10)

windows();myboot2(10000,x=sam,fun="mean",alpha=0.05,xlab="mean",col="Purple",cx=1.5) # mac quartz()

## quantile
alpha=0.05
qnorm(1-alpha/2)
qnorm(alpha/2)


```



```{r}
myboot2<-function(iter=10000,x,fun="population variance",alpha=0.02,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

invisible(list(ci=ci,fun=fun,x=x))# Some output to use if necessary
}

set.seed(30); sam=rchisq(20,df=3)


windows();myboot2(10000,x=sam,fun="mean",alpha=0.05,xlab="mean",col="Purple",cx=1.5) # mac quartz()

## quantile
alpha=0.05
qnorm(1-alpha/2)
qnorm(alpha/2)



```

```{r}
myboot2<-function(iter=10000,x,fun="population variance",alpha=0.02,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

invisible(list(ci=ci,fun=fun,x=x))# Some output to use if necessary
}


```


```{r}
myboot2<-function(iter=10000,x,fun="population variance",alpha=0.02,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

invisible(list(ci=ci,fun=fun,x=x))# Some output to use if necessary
}

set.seed(40); sam=rgamma(30,shape=2,scale=3)


windows();myboot2(10000,x=sam,fun="mean",alpha=0.05,xlab="mean",col="Purple",cx=1.5) # mac quartz()

## quantile
alpha=0.05
qnorm(1-alpha/2)
qnorm(alpha/2)





```




# Task 4 

```{r}
myboot2<-function(iter=10000,x,fun="mean",alpha=0.05,cx=1.5,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...)

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=cx)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=cx)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=cx)

(list(ci=ci,fun=fun,x=x, xstat= xstat))# Some output to use if necessary
}

sam=c(1,1,1,2,2,2,2,3,3,3,4,4) 

obj = myboot2(x=sam,fun="median") 
 
```

 The bootstrap interval estimate for the median is 1.5 to 3. 

# Task 5 

```{r}

set.seed(39)
sam=rnorm(25,mean=25,sd=10)
obj = myboot2(x = sam, fun=function(x)
{mean(x)/median(x)}, alpha = 0.05) 
  
```

```{r}
set.seed(30)
sam=rchisq(20,df=3)
obj = myboot2(x = sam, fun=function(x)
{mean(x)/median(x)}, alpha = 0.05)
```
```{r}
set.seed(40)
sam=rgamma(30,shape=2,scale=3)
obj = myboot2(x = sam, fun=function(x)
{mean(x)/median(x)}, alpha = 0.05)
```
```{r}
set.seed(10)
sam=rbeta(20,shape1=3,shape2=4)
obj = myboot2(x = sam, fun=function(x)
{mean(x)/median(x)}, alpha = 0.05)

```
# Plot with 70% intervals 

```{r}
 set.seed(39)
sam=rnorm(25,mean=25,sd=10)
obj = myboot2(x = sam, fun=function(x)
{mean(x)/median(x)}, alpha = 0.30)
```
```{r}
 set.seed(30)
set.seed(30); sam=rchisq(20,df=3)
mobj = myboot2(x = sam, fun=function(x)
{mean(x)/median(x)}, alpha = 0.30)
```

```{r}
 set.seed(40)
sam=rgamma(30,shape=2,scale=3)
obj = myboot2(x = sam, fun=function(x)
{mean(x)/median(x)}, alpha = 0.30)
```

```{r}
set.seed(10)
sam=rbeta(20,shape1=3,shape2=4)
obj = myboot2(x = sam, fun=function(x)
{mean(x)/median(x)}, alpha = 0.30)
```



# Task 6

```{r}
sam=rf(20, 15,20)
obj = myboot2(x = sam, fun = "mean", alpha = 0.20, iter = 10000)
```

```{r}

sam = rwilcox(10,20,20)
obj = myboot2(x = sam, fun = "mean", alpha= 0.20, iter= 10000) 
```

```{r}
sam = rcauchy(20, location= 0, scale= 1)
obj = myboot2(x = sam, fun= "mean" , alpha= 0.20, iter= 10000) 
```


```{r}
sam = rsignrank(10,20)
obj = myboot2(x = sam, fun= "mean" , alpha= 0.20, iter= 10000)
```





# Make 80% bootstrap intervals for mean and variance 

```{r}
sam= rcauchy(20, location= 1, scale= 1 )
obj = myboot2(iter =10000 , x= sam, fun= "var", alpha= 0.20 ) 
```
```{r}
sam = rwilcox(10,20,20)
obj = myboot2(x = sam, fun = "var", alpha= 0.20, iter= 10000)
```

```{r}
sam=rf(20, 15,20)
obj = myboot2(x = sam, fun = "var", alpha = 0.20, iter = 10000)
```
```{r}
sam = rsignrank(10,20)
obj = myboot2(x = sam, fun= "var" , alpha= 0.20, iter= 10000)
```

# Task 7 

```{r}
set.seed(68)
sam=rnorm(20,mean=10,sd=4)
obj = myboot2( x= sam, fun = "sd", alpha = 0.20, iter = 10000)
```
```{r}
set.seed(68)
sam=rnorm(20,mean=10,sd=4) 
obj = myboot2( x= sam, fun = "IQR", alpha = 0.20, iter = 10000)
```
```{r}

mp = c(1,-1)
z_a2 = qnorm(1-.05, mean=0, sd=1)


mean(sam) - mp*z_a2*sd(sam)/sqrt(20)
obj = myboot2(sam, iter=10000, fun = "mean", alpha = .05)
```
The values from the equation is pretty close to the intervals on the histogram. 


# Task 8

```{r}
library(NewPackage2022)

NewPackage2022::myboot2(sam, iter=10000, fun= "mean", alpha= 0.05)
```








