---
title: "Lab 4"
author: "Christine Gormley"
date: '`r Sys.Date()` '
output: 
  html_document: 
        toc: yes
        toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 1

```{r}
getwd()
```

# Task 2

```{r}
spruce = read.csv("SPRUCE.csv")
tail(spruce)
```
# Task 3

#Lowess Smooth Scatter Plot
```{r}
library(s20x)
trendscatter(Height~BHDiameter,f=0.5,data=spruce)

```
# Linear Model 

```{r}
spruce.lm=with(spruce,lm(Height~BHDiameter)) 
summary(spruce.lm)
```

# Find Residuals 

```{r}
height.res=residuals(spruce.lm)
summary(height.res)

```

# Finding Fitted Values
 
```{r}
fitted.res=fitted(spruce.lm)
summary(fitted.res)
```
 
```{r}
plot(x= fitted.res, y=height.res)
```
 

```{r}
trendscatter( y= height.res, x= fitted.res)
```

# What is the Shape of the Plot? 

 The shape in this plot comparing residuals verses fitted values is a curve and a downward slope of the data. This curve looks more like an upward climb of data followed by a downward fall. The other trendscatter plot was just a curved line trend in the data. 
 
 The pvalue in this case is 2.089e-09. 

```{r}
windows()
normcheck(spruce.lm,shapiro.wilk = TRUE)

```

The pvalue for this plot is 0.29.
# Residual Plot 
```{r}
plot(spruce.lm, which = 1)
```




# Task 4

# Making a Quadratic Model

```{r}
library(s20x) 
trendscatter( fitted.res,height.res)
windows()
plot(Height~BHDiameter,bg="Blue",pch=21,cex=1.2,
ylim=c(0,max(Height)),xlim=c(0,max(BHDiameter)), 
main="Spruce Height Prediction",data=spruce)
quad.lm=lm(Height~BHDiameter + I(BHDiameter^2),data=spruce)
summary(quad.lm)

coef(quad.lm)
names(quad.lm)
quad.lm$coef[2]

myplot=function(x){
 0.86089580 +1.46959217*x  -0.02745726*x^2
}
curve(myplot, lwd=2, col="purple",add=TRUE) 

```

```{r}
quadfit = fitted(quad.lm)
summary(quad.lm)
```
# Residuals vs. Fitted with a Quadratic Line
```{r}
plot(quad.lm, which=1)
```


# Normality Check 

```{r}
windows()
normcheck(quad.lm,shapiro.wilk = TRUE)
```





# Task 5


```{r}
summary(quad.lm)
```

B hat values 

Bhat sub 0 = 0.86089580

Bhat sub 1 = 1.4959217

Bhat sub 2 = -0.027457

# Making Interval Estimates 

```{r}

ciReg(quad.lm)
```
# Equation of Fitted Line

y = 0.0860896 + 1.469x - 0.0274x^2

```{r}
predict(quad.lm, data.frame(BHDiameter=c(15,18,20)))
```

```{r}
predict(quad.lm, data.frame(BHDiameter= c(3,6,8)))
```
# Value of R^2



The value for multiple R^2 in the quadratic equation model is 0.77 and the multiple R^2 for the spruce scatter plot is 0.6569. 

The adjusted R^2 for the quadratic line is 0.76 and the adjusted for the spruce scatter plot is 0.6468. 

The value for multiple R^2 for the quadratic line is a much better representation of the data because a higher percentage is explained by the plot. 


# Variability in Height

#Anova

```{r}
anova(spruce.lm)
anova(quad.lm)
anova(spruce.lm,quad.lm)
```

# Solving for TSS 

```{r}
TSS = with(spruce, sum((Height-mean(Height))^2))
TSS
```
# Solving for RSS 

```{r}
height.fit=fitted(spruce.lm)
RSS=with(spruce, sum((Height-height.fit)^2))
RSS
```
# Sovling for MSS

```{r}
MSS = with(spruce, sum((height.fit-mean(Height))^2))
MSS
```

```{r}
MSS/TSS
```


# Task 6

# Creating a Cooks Plot 

```{r}
cooks20x(quad.lm)


```

Cooks Distance is used to determine the influence or importance of a data point when conducting a regression analysis. Points with a higher distance may distort the accuracy of the plot.  

Cooks Distance tells me that certain numbers matter more to the data set than others. 

```{r}
quad2=lm(Height~BHDiameter + I(BHDiameter^2) , data=spruce[-24,])
summary(quad2)
summary(quad.lm)
```
The new object above removed the outlier number (24) according to cooks distance. After doing this the mulitple R^2 increased to 0.81. 
This is a far more accurate data representation without the outlier.
I can conclude that removing the number 24 from the data set the result was more accurate. 

# Task 7


 
 
   \begin{eqnarray}

\beta_0 +\beta_1 x_k &=& \beta_0\ - \beta_2x_k + (\beta_1+\beta_2)x_k\\ 
y&=& \beta_0 -\beta_2x_k + (\beta_1 +\beta_2)x\\
y&=& \beta_0 + \beta_1 x +\beta_1 + \beta_2(x-x_k)I(x>x_k)
\end{eqnarray} 




```{r}
sp2.df=within(spruce, X<-(BHDiameter-18)*(BHDiameter>18)) 
sp2.df

lmp=lm(Height~BHDiameter + X,data=sp2.df)
tmp=summary(lmp)
names(tmp)
myf = function(x,coef){
  coef[1]+coef[2]*(x) + coef[3]*(x-18)*(x-18>0)
}
plot(spruce,main="Piecewise regression")
myf(0, coef=tmp$coefficients[,"Estimate"])
curve(myf(x,coef=tmp$coefficients[,"Estimate"] ),add=TRUE, lwd=2,col="Blue")
abline(v=18)
text(18,16,paste("R sq.=",round(tmp$r.squared,4) ))

 
```



# Task 8

```{r}
library(MATH4753CG)

```










